---
title: "Termination Study"
author: "Joselle Abagat"
date: "October 11, 2017"
output: 
  slidy_presentation:
    font_adjustment: -1
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)

library(DT)
library(scales)
library(formattable)

source("termStudy.R")

empDT <- fread("rawdata.csv")
compDT <- fread("comphistory.csv")
termDT <- fread("termhist.csv")
mbpDT <- fread("marketpay.csv")
oc <- fread("otherComp.csv")
```

## Transmission Line Tech Termination Study 
- NOTE: Press "k" to disable mouse click
- Data current as of:

-- 10/11/2017 (employee history)

-- 10/11/2017 (termination history)

-- 5/2/2017 (rating history)


## Transmission Line Tech Turnover
```{r, warning=FALSE}
s <- subTurnOverByYear(empDT)
```
- From 2012-2016, Company X's avg turnover rate was approximately 6%; the line tech average turnover was `r mean(s$TurnOver[s$Year < 2017])`%, higher than the company average.
- Turnover has been increasing since 2014
- Using data from 2014-2016, regression analysis shows that we are predicting to lose 8 line techs in 2017. 
- To date, we are already past the 8 predicted line techs; we have lost 12. 
- Company X's turnover to date is at 5.6%.  Considering the company's low turnover rate, a job turnover at 25% thru Oct-2017 is problematic. 
```{r, warning=FALSE}
plotTurnOver(empDT)
```


## Terminated Line Techs in the Past Five Years
```{r, echo=FALSE}
term <- termedLineTechs(empDT, termDT)
termCount <- term[ , .N, ActionCode][, 2]
VolPercent <- percent(term[grep("RESIGNED", PA52ReasonCodeDesc), .N]/nrow(term))
involPercent <- percent(term[grep("INVOL", PA52ReasonCodeDesc), .N]/nrow(term))
nResigned <- term[grep("RESIGN", PA52ReasonCodeDesc), .N]
nMoreMoney <- term[PA52ReasonCodeDesc == "RESIGNED - MORE MONEY", .N]
```
- Plot of the terminated line techs by reason code is provided below
- Total number of terminated line techs in the last 5 years: `r nrow(term)`
- `r VolPercent` of the line techs terminated voluntarily ("RESIGNED"")
- `r percent(nMoreMoney/nrow(term))` of terminations was due to desire for more income
- `r involPercent` was terminated involuntarily

```{r}
plotTermLineTechsReasonCode(term)
```

## Terminated Line Techs in the Past Five Years by Job Code
```{r}
plotTermLineTechsJobCode(empDT)
```

## Line Tech Current Compensation Study
- Statistical box plot of current line tech salary by Job Code in comparison to market pay (total compensation and base)
- The box plot provides the min, max, median, 25th and 75th percentile
- The plot also includes the avg base salary and avg total compensation based on the base salary
```{r, warning=FALSE}
plotCurLineTechComp(empDT, mbpDT, oc)
```


## End